biclaR

### 2022-12-04 code/biclarwww/index.Rmd
minor adjustments website
solve Vila Franca Xira

municipios_index = readRDS(url("https://github.com/U-Shift/biclar/releases/download/0.0.1/MUNICIPIOSgeo.Rds")) %>% #it was counties_index -> change to a table with mode statistics!
  # dplyr::mutate(county_name = stringr::str_to_title(Concelho)) %>% #maiusculas
  dplyr::rename(Municipio = Concelho) %>%
  # dplyr::mutate(Municipio = stringr::str_to_sentence(Municipio)) %>% #minusculas
  dplyr::mutate(url = paste0(
  "<a href='", tolower(Municipio) , "/' target='_blank'>",  Municipio,  "</a>"
)) 
municipios_index = sf::st_as_sf(municipios_index)
```

@@

@@

------------------------------------------------------------------------

@@

*   Grupo de Trabalho: ...
*   Conselho Consultuvo: ....
*   CycleStreets
*   r5r

>>>>

municipios_index = readRDS(url("https://github.com/U-Shift/biclar/releases/download/0.0.1/MUNICIPIOSgeo.Rds")) %>% #it was counties_index -> change to a table with mode statistics!
  # dplyr::mutate(county_name = stringr::str_to_title(Concelho)) %>% #maiusculas
  dplyr::rename(Municipio = Concelho) %>%
  # dplyr::mutate(Municipio = stringr::str_to_sentence(Municipio)) %>% #minusculas
  dplyr::mutate(url = paste0(
  "<a href='", tolower(Municipio) , "/' target='_blank'>",  Municipio,  "</a>"
))

municipios_index$url[Municipio == "Vila Franca de Xira"] = paste0("<a href='vfxira/' target='_blank'>",  Municipio,  "</a>")

municipios_index = sf::st_as_sf(municipios_index)

@@

```{r}
#read data
transit_all = sf::st_read("https://github.com/U-Shift/biclar/releases/download/0.0.1/transit.gpkg", quiet = TRUE)

library(tmap)
tmap_mode("view")

tm_shape(transit_all) +
  tm_sf(col = "mode", size = 0.3)
```

@@

<!-- ------------------------------------------------------------------------ -->

@@

*   Grupo de Trabalho: ...
*   Conselho Consultuvo: ....
*   Matheus Correia, OpenStreetMap Portugal
*   CycleStreets
*   r5r
